Novel Methods for Characterizing Peaks from Direct Injection FT-MS Experiments

### 2022-03-02 doc/peakcharacterization_manuscript.Rmd
moving things around

---
title: "Novel Methods for Characterizing Peaks from Direct Injection FT-MS Experiments"
author: "Robert M Flight, Joshua M Mitchell, Hunter NB Moseley"
date: "`r Sys.time()`"
output: 
  redoc::redoc
---

>>>>

---
title: "Novel Methods for Characterizing Peaks from Direct Injection FT-MS Experiments"
author: "Robert M Flight, Joshua M Mitchell, Hunter NB Moseley"
date: "`r Sys.time()`"
output: 
  word_document:
    keep_md: true
---
